Model for DES Type Ia Supernova Cosmology Analysis

### 2015-09-10 doc/model.tex
current status of code and output now in document

\section{Simple Example}
\subsection{Model}
\label{example:sec}
A simplified version of the above model,
\begin{equation}
p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_G|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}),
\end{equation}
is examined in this section.
The measurements: 
\begin{itemize}
\item $\mathit{ADU}$ are measured counts at peak brightness.
\item ${{T}}_S$, ${{z}}_S$ are spectroscopic type and redshift for a subset of transients.
\item $\theta_G$ is the redshift of the galaxy identified as the transient host.
\end{itemize}
The model parameters:
\begin{itemize}
\item $\Omega_M$, $w$ are the parameters of a flat dark-energy cosmology.
\item $\theta_r$ describe the fraction of transients that are SN~Ia, independent
of host-galaxy properties.
\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$ are
the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak.
Light-curve shape and color are not considered in this simple model.
\end{itemize}

@@

\subsubsection{Model for the {\it obs} set data}
The modeling of data from the {\it obs} set, which has
spectroscopic observations $T_S$ and redshift
$z_S$, is described as follows.  We are interested in
\begin{align}
p(\mathit{ADU}, {{T}}_S,{{z}}_S|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  &=\sum_T \int_z dz\,
p(\mathit{ADU}, {{T}}_S,{{z}}_S, T, z| \ldots)\\
&= \sum_T \int_z dz\,
p(\mathit{ADU}, {{T}}_S,{{z}}_S| T, z,\dots) P(T,z | \ldots)
\end{align}

A direct association of spectroscopic redshift and type are made so that
\begin{align}
p(z_S|z) &= \delta(z_S-z)\\
p(T_S|T) &= \delta(T_S-T),
\label{specz:eqn}
\end{align}
so that
\begin{align}
p(\mathit{ADU}, {{T}}_S,{{z}}_S|  \ldots) &= 
p(\mathit{ADU}| T_S, z_s,\dots) P(T_S,z_S | \ldots)
\end{align}

The first term: Given the redshift
and transient type, the brightness of the underlying population
is modeled as being drawn from a standard candle
with luminosity $4\pi\alpha_X$ and intrinsic magnitude dispersion  $\sigma_X$:
\begin{equation}
\mathit{ADU}| T_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
\end{equation}
where $\mathcal{N}_{\ln}$ is the log-normal distribution and $d_L$ is the luminosity distance.

The subset of objects that enters our analysis comes from a truncated distribution:
\begin{itemize}
\item For transients in set $T_S=1$:
\begin{equation}
\mathit{ADU} | \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)}{P_{Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
\label{adusnIa:eqn}
\end{equation}
\item For transients in set $T_S=0$:
\begin{equation}
\mathit{ADU} | \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right)}{P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)},
\label{adunonIa:eqn}
\end{equation}
\end{itemize}
where the normalization factor is the complementary cumulative distribution function
for the corresponding log-normal distribution.
It is understood that $p(\mathit{ADU}<\mathit{ADU}_0)=0$ is never evaluated.

The second term is redshift and type probabilities.  In our model we adopt
a flat prior on the redshift distribution.
The underlying relative rates between SNe~Ia and non-Ia are modeled
as being linear in redshift parameterized by the
its value at $z=0$ and $1.1 \times z_{max}$, 
\begin{equation}
\hat{\theta}_{r}=\theta_{r0}+z\left(\frac{\theta_{r1}-\theta_{r0}}{1.1 \times z_{max}}\right).
\end{equation}
The relative rate for SN~Ia discovery is then
\begin{equation}
\theta_{r}=\frac{\hat{\theta}_{r}}{\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0) + (1-\hat{\theta}_{r})P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
\end{equation}
The spectroscopic classifications are drawn from
\begin{equation}
T_S | \theta_{r0}, \theta_{r1} \sim \text{Bernoulli}(\theta_r).
\end{equation}

@@

We now consider the modeling of data from the  {\it mis}
set that has no spectroscopic confirmation.
The redshift measurement is treated as follows:
For each transient there are two galaxies identified as
the potential host, one ($\theta_{G1}$) with high probability $P_{host}$
of being the host and the other
($\theta_{G2}$) at lower $(1-P_{host})$ probability.
In the model, the
true host redshift is $z$ and that of the interloping galaxy is $z_N$.
\begin{equation}
P(\theta_{G1},\theta_{G2}|z, z_N) =
	P_{host}\delta(z-\theta_{G1})\delta(z_N-\theta_{G2}) +
	(1-P_{host}) \delta(z-\theta_{G2})\delta(z_N-\theta_{G1}).
\end{equation}

The underlying distribution for counts at peak brightness $\mathit{ADU}$
is
\begin{multline}
p(\mathit{ADU}, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}) \\
 \sum_{z, T}  p(\mathit{ADU, \theta_{G1}, \theta_{G2}}| z , z_H, T \ldots)P(z, T|\ldots).
\label{adumis:eqn}
\end{multline}

The marginalization of Eqn.~\ref{adumis:eqn} thus gives for a transient with $\theta_{G1}$,
$\theta_{G2}$ an underlying distribution of counts of
 \begin{multline}
\mathit{ADU}| \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \\
 \sim  P_{host} \left[\theta_r \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(\theta_{G1})}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)
+\left(1-\theta_r\right)
\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(\theta_{G1})}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right) \right] \\
 + (1-P_{host})\left[ \theta_r \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(\theta_{G2})}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right) 
 + \left(1-\theta_r\right)
\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(\theta_{G2})}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right) \right],
\label{adumis2:eqn}
\end{multline}
where again we adopt a flat prior in redshift.

The distribution of $\mathit{ADU}$ for our sample is a truncated version of the
underlying distribution.  
For our analysis, we use the distribution in  Eqn.~\ref{adumis2:eqn} normalized by
the complementary cumulative distribution function
\begin{equation}
P(\mathit{ADU}>\mathit{ADU}_0|\ldots) = \int_{\mathit{ADU}_0}^{\infty} p(\mathit{ADU}|\Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})d\mathit{ADU}
\end{equation}
for a detection threshold of $\mathit{ADU}_0$.

@@

The results that follow are based on the parameter
choices:
\begin{itemize}
\item Cosmological parameters $\Omega_M=0.28$, $w=-1$.
\item Type~Ia supernovae with intrinsic dispersion $\sigma_{SNIa}=0.1$.
\item Non-Ia supernovae 2 magnitudes fainter than SNe~Ia with intrinsic
dispersion $\sigma_{non-Ia}=1$.
\item $\theta_r=r_0 + (r_1-r_0)z/2.1$ for a constant relative fraction of SNe~Ia where $r_1=0.2$,
$r_0=0.95$.
\item 2000 transients distributed by co-moving volume in the range $0.1<z<1.4$.
\item Detection threshold at approximately the mean brightness SN~Ia at $z=1.2$.
\item $z_{min}=0.1/1.1$ and $z_{max}=1.4\times 1.1$ is the range of possible misassigned
host redshift.
\item $P_{host}=0.98$ for the probability of correct host-galaxy assignment.
\item Accumulated spectra for 20\%, 60\%, and 100\% of discovered transients.
\end{itemize}

In our simulated data sets, the
pdf for the redshift of the second galaxy is approximately uniform in volume:
\begin{equation}
\frac{3 z_N^2}{z_{max}^3 - z_{min}^3}.
\end{equation}

A prior is applied to the SN~Ia absolute magnitude
\begin{equation}
\alpha_{SNIa} \sim \ln\mathcal{N}\left(\ln\left(\alpha^0_{SNIa}\right),\frac{\ln{10}}{2.5}0.02\right),
\end{equation}
where $\alpha^0_{SNIa}$ is the true input luminosity.

The simulated data are analyzed using 
\citet{stan-software:2015}, a
a probabilistic programming language for
inference of Bayesian models with Hamiltonian Monte Carlo.  There are
four chains run, each with 50,000 samples then thinned by 5.  Half the links
are used for burnin, so ultimately 20,000 links are used as draws from the posterior.

\subsubsection{SN~Ia Only}
A classical analysis would only include confirmed SNe~Ia with a definitive
redshift. The realization of simulated data has 415 Type~Ia supernovae.
Results of the analysis of a pure SN~Ia sample with no
host misclassification are presented:  Figure~\ref{contour.ia_only:fig}
shows the posteriors for  $\Omega_M$--$w$ and Table~\ref{ia_only:tab} the
credible equal-tailed intervals for $w$.  The true $w=-1$ is within
the 0.58 credible interval. (Note that $w$ is the parameter
of most interest for the experiment.)

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour..ia_only.500}.pdf} \newline
\caption{Probability distribution function for $\Omega_M$--$w$ for only SNe~Ia
   all with spectra.
   Solid lines represent the input cosmology.  Dashed lines in the
   histograms are the 0.16 and 0.86 quantiles. 
   \label{contour.ia_only:fig}}
\end{figure}

\begin{table}
\centering
\begin{tabular}{|c|cc|}
\hline
\%-ile & $w$ range & $\Delta w$\\ \hline
$0.68$ & $[-1.254, -0.975]$ & $0.279$ \\
$0.90$ & $[-1.347, -0.889]$ & $0.458$ \\
$0.95$ & $[-1.396, -0.846]$ & $0.550$ \\
\hline
\end{tabular}
\caption{Credible intervals of $w$ using the SNe~Ia only with spectroscopic
observations.\label{ia_only:tab}}
\end{table}

\subsubsection{Full Sample: Varying Spectroscopic Completeness}
We now turn to the full sample of SNe~Ia and non-Ia's.  Recall that our simple
model treats the non-Ia's in the sample
as standard candles with a large (1 mag) intrinsic dispersion.

Results for the $\Omega_M$--$w$ posterior for the
case of 40\%, 70\%, and 100\% spectroscopic completeness
are shown in Figures~\ref{contour.200:fig}, \ref{contour.350:fig}, and
\ref{contour.500:fig} respectively.
The credible intervals
of $w$ for are given in Table~\ref{compare:tab}, with
the input $w=-1$ within the 0.65, 0.49, and 0.47  intervals
respectively.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.200}.pdf} 
   \caption{Probability distribution function for $\Omega_M$--$w$ for:
    SNe~Ia and non-Ia with 40\%  spectroscopic completeness.
   \label{contour.200:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.350}.pdf} 
   \caption{Probability distribution function for $\Omega_M$--$w$ for
    SNe~Ia and non-Ia with 70\%  spectroscopic completeness.
   \label{contour.350:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.500}.pdf} 
   %\includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour.200}.pdf}    
   \caption{Probability distribution function for $\Omega_M$--$w$ for
    SNe~Ia and non-Ia with 100\%  spectroscopic completeness.
   \label{contour.500:fig}}
\end{figure}

\begin{table}[htbp] 
\centering
\begin{tabular}{|cc|cc|}
\hline
\# Spectra & \%-ile & $w$ range & $\Delta$\\ \hline
200& $0.68$ & $[-1.284, -0.991]$ & $0.293$ \\
200& $0.90$ & $[-1.385, -0.900]$ & $0.485$ \\
200& $0.95$ & $[-1.435, -0.860]$ & $0.575$ \\
350& $0.68$ & $[-1.243, -0.952]$ & $0.291$ \\
350& $0.90$ & $[-1.339, -0.858]$ & $0.481$ \\
350& $0.95$ & $[-1.390, -0.817]$ & $0.573$ \\
500& $0.68$ & $[-1.236, -0.948]$ & $0.289$ \\
500& $0.90$ & $[-1.336, -0.861]$ & $0.475$ \\
500& $0.95$ & $[-1.385, -0.815]$ & $0.570$ \\
\hline
\end{tabular}
\caption{Credible intervals of $w$ given different levels of spectroscopy.  \label{compare:tab}}
\end{table}

As would be expected, the better the spectroscopic completeness, the less bias
and smaller uncertainties that are obtained.

>>>>

\section{Simple Example}
\subsection{Model}
\label{example:sec}
A simplified version of the above model,
\begin{equation}
p(\mathit{ADU}, {{T}}_S,{{z}}_S, \theta_G|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}),
\end{equation}
is examined in this section.
The measurements: 
\begin{itemize}
\item $\mathit{ADU}$ are measured counts at peak brightness.
\item ${{T}}_S$, ${{z}}_S$ are spectroscopic type and redshift for a subset of transients.
\item $\theta_G$ are the redshift of the galaxy identified as the transient host.
\end{itemize}
The model parameters:
\begin{itemize}
\item $\Omega_M$, $w$ are the parameters of a flat dark-energy cosmology.
\item $\theta_r$ describe the fraction of transients that are SN~Ia, independent
of host-galaxy properties.
\item $\alpha_{Ia}$, $\sigma_{Ia}$, $\alpha_{\mathit{non-Ia}}$, $\sigma_{\mathit{non-Ia}}$ are
the luminosity (times $4\pi$) and intrinsic dispersion for SNe~Ia and non-Ia at peak.
Light-curve shape and color are not considered in this simple model.
\end{itemize}

@@

\subsubsection{Model for the {\it obs} set data}
The modeling of data from the {\it obs} set, which has
spectroscopic observations $T_S$ and redshift
$z_S$, is described as follows.  We are interested in
\begin{align}
p(\mathit{ADU}, {{T}}_S,{{z}}_S|  \Omega_M, w, \theta_r,\alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  &=\sum_T \int_z dz\,
p(\mathit{ADU}, {{T}}_S,{{z}}_S, T, z| \ldots)\\
&= \sum_T \int_z dz\,
p(\mathit{ADU}, {{T}}_S,{{z}}_S| T, z,\dots) p(T,z | \ldots)
\end{align}

A direct association of spectroscopic redshift and type are made so that
\begin{align}
p(z_S|z) &= \delta(z_S-z)\\
p(T_S|T) &= \delta(T_S-T),
\label{specz:eqn}
\end{align}
so that
\begin{align}
p(\mathit{ADU}, {{T}}_S,{{z}}_S|  \ldots) &= 
p(\mathit{ADU}| T=T_S, z=z_s,\dots) P(T_S| z= z_S , \ldots) p(z_S|\ldots).
\label{obs:eqn}
\end{align}
We remark that in a flux limited survey, the pdf's for the data are truncated versions of the universal
pdf's of the observables.

The first term describes the expected counts. Given the redshift
and transient type, the brightness of the underlying population
is modeled as being drawn from a standard candle
with luminosity $4\pi\alpha_X$ and intrinsic magnitude dispersion  $\sigma_X$:
\begin{equation}
\mathit{ADU}| T_S, z_S, \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{T_S}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{T_S}\right),
\end{equation}
where $\mathcal{N}_{\ln}$ is the log-normal distribution and $d_L$ is the luminosity distance.

The subset of objects that enters our analysis comes from a truncated distribution:
\begin{itemize}
\item For transients in set $T_S=1$:
\begin{equation}
\mathit{ADU} | T_S=1, z_S, \Omega_M, w, \alpha_{Ia},\sigma_{Ia} \sim
\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{Ia}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{Ia}\right)}{P_{Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
\label{adusnIa:eqn}
\end{equation}
\item For transients in set $T_S=0$:
\begin{equation}
\mathit{ADU} | T_S=0, z_S, \Omega_M, w, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}}\sim 
\frac{\mathcal{N}_{\ln}\left(\ln{\left(\frac{\alpha_{\mathit{non-Ia}}}{d_L^2(z_S;\Omega_M, w)}\right)}, \frac{\ln{10}}{2.5}\sigma_{\mathit{non-Ia}}\right)}{P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)},
\label{adunonIa:eqn}
\end{equation}
\end{itemize}
where the normalization factor is the complementary cumulative distribution function
for the corresponding log-normal distribution.
It is understood that $p(\mathit{ADU}<\mathit{ADU}_0)=0$ is never evaluated.

The second term gives the type probability. In our model,
the underlying relative rates between SNe~Ia and non-Ia is linear in redshift,
 parameterized by the
its value at $z=0$ and $1.1 \times z_{max}$, 
\begin{equation}
\hat{\theta}_{r}=\theta_{r0}+z\left(\frac{\theta_{r1}-\theta_{r0}}{1.1 \times z_{max}}\right).
\end{equation}
The relative rate for SN~Ia discovery for the truncated distribution is
\begin{equation}
\theta_{r}=\frac{\hat{\theta}_{r}}{\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0) + (1-\hat{\theta}_{r})P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)}.
\end{equation}
The spectroscopic classifications are drawn from
\begin{equation}
T_S | \Omega_M, w, \theta_{r0}, \theta_{r1} , \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}} \sim \text{Bernoulli}(\theta_r).
\end{equation}
Although the underlying type distribution depends only on $ \theta_{r0}$ and $ \theta_{r1}$,  
the observed truncated distribution does depend on the other parameters through 
$P_{X}(\mathit{ADU} > \mathit{ADU}_0)$.

The third term is the redshift distribution of transient discoveries.
In our model we adopt
a redshift distribution of transients in the universe
\begin{equation}
P(z) \propto z^2.
\end{equation}
The redshift distribution of discovered transients is then
\begin{equation}
P(z) = \left(\int_{z_{min}}^{z_{max}} dz'\, z'^2\left( 
\hat{\theta}_{r}P_{Ia}(\mathit{ADU} > \mathit{ADU}_0) + (1-\hat{\theta}_{r})P_{non-Ia}(\mathit{ADU} > \mathit{ADU}_0)
\right)\right)^{-1}z^2.
\end{equation}

In the presented model, the data from different transients are independent.

@@

We now consider the modeling of data from the  {\it mis}
set that has no spectroscopic confirmation.
The redshift measurement is treated as follows:
For each transient there are two galaxies identified as
the potential host, one ($\theta_{G1}$) with high probability $P_{host}$
of being the host and the other
($\theta_{G2}$) at lower $(1-P_{host})$ probability.
In the model, the
true host redshift is $z$ and that of the interloping galaxy is $z_N$.
\begin{equation}
P(\theta_{G1},\theta_{G2}|z, z_N) =
	P_{host}\delta(z-\theta_{G1})\delta(z_N-\theta_{G2}) +
	(1-P_{host}) \delta(z-\theta_{G2})\delta(z_N-\theta_{G1}).
\end{equation}
As for the {\it obs} set, the redshifts of the supernova
 and neighbor are drawn from distributions $P(z) \propto z^2$, $P(z_N) \propto z^2_N$.

The data likelihood is 
\begin{multline}
p(\mathit{ADU}, \theta_{G1}, \theta_{G2} | \Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})  \\
= \sum_{T}\int_{z,z_N} dz\,dz_N \, p(\mathit{ADU, \theta_{G1}, \theta_{G2}}| z , z_N, T, \ldots)P(T| z, z_N,\ldots) P(z, z_N|\ldots)\\
 =\sum_{T} \int_{z,z_N} dz\,dz_N\, p(\mathit{ADU}| z ,T, \ldots)p(\theta_{G1}, \theta_{G2}| z , z_N) P(T| z, \ldots) P(z, z_N|\ldots)\\
= \sum_{T} P_{host} p(\mathit{ADU}| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) P(\theta_{G1},\theta_{G2}|\ldots) \\
 +  (1-P_{host}) p(\mathit{ADU}| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots) P(\theta_{G2},
 \theta_{G1}|\ldots)\\
\propto \sum_{T} P_{host} p(\mathit{ADU}| z=\theta_{G1} ,T, \ldots) P(T| z=\theta_{G1}, \ldots) \\
 +  (1-P_{host}) p(\mathit{ADU}| z=\theta_{G2} ,T, \ldots) P(T| z=\theta_{G2}, \ldots),
\label{adumis:eqn}
\end{multline}
where we take advantage of the fact that
$P(\theta_{G1}, \theta_{G2} | \ldots) = P(\theta_{G2}, \theta_{G1} | \ldots)$ does
not have parameter dependence.

The distribution of $\mathit{ADU}$ for our sample is a truncated version of the
underlying distribution.  
For our analysis, we use the distribution in  Eqn.~\ref{adumis:eqn} normalized by
the complementary cumulative distribution function
\begin{equation}
P(\mathit{ADU}>\mathit{ADU}_0, \theta_{G1}, \theta_{G2}|\ldots) = \int_{\mathit{ADU}_0}^{\infty} p(\mathit{ADU}, \theta_{G1}, \theta_{G2}|\Omega_M, w, \theta_r, \alpha_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\sigma_{\mathit{non-Ia}})d\mathit{ADU}
\end{equation}
for a detection threshold of $\mathit{ADU}_0$.

@@

The results that follow are based on the parameter
choices:
\begin{itemize}
\item Cosmological parameters $\Omega_M=0.28$, $w=-1$.
\item Type~Ia supernovae with intrinsic dispersion $\sigma_{SNIa}=0.1$.
\item Non-Ia supernovae 2 magnitudes fainter than SNe~Ia with intrinsic
dispersion $\sigma_{non-Ia}=1$.
\item $\theta_r=r_0 + (r_1-r_0)z/1.54$ for a constant relative fraction of SNe~Ia where $r_1=0.2$,
$r_0=0.95$.
\item 2000 transients distributed by co-moving volume in the range $0.1<z<1.4$.
\item Detection threshold at approximately the mean brightness SN~Ia at $z=1.2$.
\item $z_{min}=0.1/1.1$ and $z_{max}=1.4\times 1.1$ is the range of possible misassigned
host redshift.
\item $P_{host}=0.98$ for the probability of correct host-galaxy assignment.
\item Accumulated spectra for 20\%, 60\%, and 100\% of discovered transients.
\end{itemize}

A prior is applied to the SN~Ia absolute magnitude and intrinsic dispersion
\begin{align}
\alpha_{SNIa} & \sim \mathcal{N}_{\ln}\left(\ln\left(\alpha^0_{SNIa}\right),\frac{\ln{10}}{2.5}0.02\right)\\
\sigma_{SNIa} & \sim \mathcal{N}_{\ln}\left(\ln\left(0.1\right),0.1\right),
\end{align}
where $\alpha^0_{SNIa}$ is the true input luminosity.

The simulated data are analyzed using 
\citet{stan-software:2015}, a
a probabilistic programming language for
inference of Bayesian models with Hamiltonian Monte Carlo.

\subsubsection{Results}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000..noMalm.1.0}.pdf} \newline
\caption{Probability distribution function for $\Omega_M$--$w$,
 100\% spectroscopy no Malmquist bias.
   Solid lines represent the input cosmology.  Dashed lines in the
   histograms are the 0.16 and 0.86 quantiles. 
   \label{contour1:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000.1.0}.pdf} \newline
\caption{Probability distribution function for $\Omega_M$--$w$,
 100\% spectroscopy with Malmquist bias.
   \label{contour2:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000.0.6}.pdf} \newline
\caption{Probability distribution function for $\Omega_M$--$w$,
 60\% spectroscopy with Malmquist bias.
   \label{contour3:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000.0.2}.pdf} \newline
\caption{Probability distribution function for $\Omega_M$--$w$,
 20\% spectroscopy with Malmquist bias.
   \label{contour4:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[scale=0.35]{/Users/akim/project/abc/results/temp/{contour..2000..noMalm.0.2}.pdf} \newline
\caption{Probability distribution function for $\Omega_M$--$w$,
 20\% spectroscopy without Malmquist bias.
   \label{contour4:fig}}
\end{figure}

\begin{table}
\centering
\begin{tabular}{cc|c|cc|}
\hline
ADU0&\% Spec&\%-ile & $w$ range & $\Delta w$\\ \hline
0 & 100 &$0.68$ & $[-1.174, -0.982]$ & $0.192$ \\
&&$0.90$ & $[-1.239, -0.923]$ & $0.316$ \\
&&$0.95$ & $[-1.267, -0.894]$ & $0.373$ \\ \hline
0.2 & 100&$0.68$ & $[-1.156, -0.972]$ & $0.184$ \\
&&$0.90$ & $[-1.222, -0.912]$ & $0.309$ \\
&&$0.95$ & $[-1.255, -0.883]$ & $0.372$ \\ \hline
0.2&60&$0.68$ & $[-1.209, -1.014]$ & $0.195$ \\
&&$0.90$ & $[-1.275, -0.955]$ & $0.321$ \\
&&$0.95$ & $[-1.309, -0.924]$ & $0.385$ \\ \hline
0&20&$0.68$ & $[-1.226, -1.032]$ & $0.194$ \\
&&$0.90$ & $[-1.289, -0.969]$ & $0.320$ \\
&&$0.95$ & $[-1.322, -0.942]$ & $0.379$ \\ \hline
0.2& 20&$0.68$ & $[-1.229, -1.033]$ & $0.196$ \\
&&$0.90$ & $[-1.294, -0.972]$ & $0.322$ \\
&&$0.95$ & $[-1.323, -0.943]$ & $0.380$ \\
\hline
\end{tabular}
\caption{Credible intervals of $w$ using the SNe~Ia only with spectroscopic
observations.\label{ia_only:tab}}
\end{table}
%\subsubsection{SN~Ia Only}
%A classical analysis would only include confirmed SNe~Ia with a definitive
%redshift. The realization of simulated data has 415 Type~Ia supernovae.
%Results of the analysis of a pure SN~Ia sample with no
%host misclassification are presented:  Figure~\ref{contour.ia_only:fig}
%shows the posteriors for  $\Omega_M$--$w$ and Table~\ref{ia_only:tab} the
%credible equal-tailed intervals for $w$.  The true $w=-1$ is within
%the 0.58 credible interval. (Note that $w$ is the parameter
%of most interest for the experiment.)
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour..ia_only.500}.pdf} \newline
%\caption{Probability distribution function for $\Omega_M$--$w$ for only SNe~Ia
%   all with spectra.
%   Solid lines represent the input cosmology.  Dashed lines in the
%   histograms are the 0.16 and 0.86 quantiles. 
%   \label{contour.ia_only:fig}}
%\end{figure}
%\begin{table}
%\centering
%\begin{tabular}{|c|cc|}
%\hline
%\%-ile & $w$ range & $\Delta w$\\ \hline
%$0.68$ & $[-1.254, -0.975]$ & $0.279$ \\
%$0.90$ & $[-1.347, -0.889]$ & $0.458$ \\
%$0.95$ & $[-1.396, -0.846]$ & $0.550$ \\
%\hline
%\end{tabular}
%\caption{Credible intervals of $w$ using the SNe~Ia only with spectroscopic
%observations.\label{ia_only:tab}}
%\end{table}
%\subsubsection{Full Sample: Varying Spectroscopic Completeness}
%We now turn to the full sample of SNe~Ia and non-Ia's.  Recall that our simple
%model treats the non-Ia's in the sample
%as standard candles with a large (1 mag) intrinsic dispersion.
%Results for the $\Omega_M$--$w$ posterior for the
%case of 40\%, 70\%, and 100\% spectroscopic completeness
%are shown in Figures~\ref{contour.200:fig}, \ref{contour.350:fig}, and
%\ref{contour.500:fig} respectively.
%The credible intervals
%of $w$ for are given in Table~\ref{compare:tab}, with
%the input $w=-1$ within the 0.65, 0.49, and 0.47  intervals
%respectively.
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.200}.pdf} 
%   \caption{Probability distribution function for $\Omega_M$--$w$ for:
%    SNe~Ia and non-Ia with 40\%  spectroscopic completeness.
%   \label{contour.200:fig}}
%\end{figure}
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.350}.pdf} 
%   \caption{Probability distribution function for $\Omega_M$--$w$ for
%    SNe~Ia and non-Ia with 70\%  spectroscopic completeness.
%   \label{contour.350:fig}}
%\end{figure}
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[scale=0.40]{/Users/akim/project/abc/results/{contour.500}.pdf} 
%   %\includegraphics[scale=0.55]{/Users/akim/project/abc/results/{contour.200}.pdf}    
%   \caption{Probability distribution function for $\Omega_M$--$w$ for
%    SNe~Ia and non-Ia with 100\%  spectroscopic completeness.
%   \label{contour.500:fig}}
%\end{figure}
%\begin{table}[htbp] 
%\centering
%\begin{tabular}{|cc|cc|}
%\hline
%\# Spectra & \%-ile & $w$ range & $\Delta$\\ \hline
%200& $0.68$ & $[-1.284, -0.991]$ & $0.293$ \\
%200& $0.90$ & $[-1.385, -0.900]$ & $0.485$ \\
%200& $0.95$ & $[-1.435, -0.860]$ & $0.575$ \\
%350& $0.68$ & $[-1.243, -0.952]$ & $0.291$ \\
%350& $0.90$ & $[-1.339, -0.858]$ & $0.481$ \\
%350& $0.95$ & $[-1.390, -0.817]$ & $0.573$ \\
%500& $0.68$ & $[-1.236, -0.948]$ & $0.289$ \\
%500& $0.90$ & $[-1.336, -0.861]$ & $0.475$ \\
%500& $0.95$ & $[-1.385, -0.815]$ & $0.570$ \\
%\hline
%\end{tabular}
%\caption{Credible intervals of $w$ given different levels of spectroscopy.  \label{compare:tab}}
%\end{table}
%As would be expected, the better the spectroscopic completeness, the less bias
%and smaller uncertainties that are obtained.
